---
title: "Pre-work"
---

A portion of this workshop will be conducted in the Posit Cloud environment. Posit Cloud allows us all to work in the exact same environment with the same version of R, R packages, and directory of files. .

Please create a login to the Posit Cloud instance of this workshop here:

**[https://posit.cloud/content/7872027](https://posit.cloud/content/7872027){target="_blank"}**


**Alternative**

If you are struggling using Posit Cloud, you can download the materials locally on your machine.

Note that the presenter will **NOT** be able to help you with local computer problems during the workshop. To do this you will need the following to do the following prior to the workshop:

-   Recent version of **R**

-   Recent version of **RStudio**

-   Recent version of packages used in this workshop:

``` {r}
#| eval: false

pkgs <- c("tidyverse", "readxl", "summarytools", "janitor", "pointblank")

install.packages(pkgs)

```

-   Get the project on your machine. Fill in `destdir` with the location where you want to download the project. Delete that argument if you want it to default to your Desktop.

```{r}
#| eval: false

# install.packages("usethis")
usethis::use_course(
    "https://github.com/Cghlewis/ncme-data-cleaning-workshop/raw/main/exercises/exercises.zip",
    destdir = "___")
```

## R and RStudio

For this workshop it is assumed that you are comfortable navigating the RStudio environment and that you have some understanding of things like packages, functions, objects, file paths, and R syntax. If you need any refreshers, I recommend reviewing the following materials.

- [Getting Started with R](https://rfortherestofus.com/courses/getting-started)
- [What They Forgot to Teach You About R](https://rstats.wtf/source-and-blank-slates) (In particular, the "A holistic workflow" section)
- [R and Tidyverse for working with data](R and the Tidyverse for working with data)
- [R Software Handbook](https://bookdown.org/aschmi11/RESMHandbook/)


## Tidyverse

If you're new to the {tidyverse}, here are some materials I recommend reviewing before the workshop.

- [R for Data Science](https://r4ds.hadley.nz/) 
- [Tidyverse Skills for Data Science](https://jhudatascience.org/tidyversecourse/)
